\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Yashwant Ponnaganti} \\ \vspace{1pt}
    \small 781-813-0396 $|$ \href{mailto:yash.ponnaganti@gmail.com}{\underline{yash.ponnaganti@gmail.com}} $|$ 
    \href{https://linkedin.com/in/yashwant-ponnaganti}{\underline{linkedin.com/in/yashwant-ponnaganti}} $|$
    \href{https://github.com/yashwant-creator}{\underline{github.com/yashwant-creator}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Maryland, College Park}{College Park, MD}
      {Bachelor of Science in Computer Science (Machine Learning Specialization)}{Expected May 2028}
    \resumeSubheading
      {Double Major: Applied Mathematics}{}
      {Presidential Scholarship Recipient}{}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {ML Engineering Intern}{June 2025 -- Present}
      {Brown University \& University of Rhode Island}{Remote}
      \resumeItemListStart
        \resumeItem{Built a Retrieval-Augmented Generation (RAG) chatbot for Polycystic Kidney Disease support, processing 100+ research papers using FAISS embeddings.}
        \resumeItem{Developed a scalable, low-latency asynchronous backend for real-time query responses, enhancing user experience.}
        \resumeItem{Collaborated with cross-functional teams to integrate OpenAI GPT-4o-mini for advanced language processing.}
      \resumeItemListEnd

    \resumeSubheading
      {Computer Hardware Engineering Intern}{June 2024 -- Aug 2024}
      {University of Rhode Island, Biomedical Engineering}{Kingston, RI}
      \resumeItemListStart
        \resumeItem{Developed a smart bottle accessory for real-time hydration reminders, improving user hydration habits.}
        \resumeItem{Conducted an international market survey with 90+ participants to assess product-market fit, guiding product development.}
        \resumeItem{Presented the prototype at IEEE MIT URTC 2024, receiving positive feedback from industry experts.}
      \resumeItemListEnd

    \resumeSubheading
      {ML Engineering Intern}{June 2023 -- Aug 2023}
      {University of Rhode Island, Biomedical Engineering}{Kingston, RI}
      \resumeItemListStart
        \resumeItem{Developed a Human Activity Recognition (HAR) model using smartwatch data to predict ADHD onset in children (ages 7–11).}
        \resumeItem{Implemented feature engineering and regression algorithms for accurate activity tracking, achieving high prediction accuracy.}
        \resumeItem{Utilized Python and Scikit-learn for model development, enhancing data processing efficiency.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Smart Hydration System} $|$ \emph{Arduino, Sensors, Embedded Systems}}{June 2024 -- Aug 2024}
          \resumeItemListStart
            \resumeItem{Engineered a smart hydration system using Arduino and sensors to provide real-time hydration reminders.}
            \resumeItem{Integrated haptic feedback and LED indicators for user notifications, enhancing user interaction.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{ADHD Prediction Model} $|$ \emph{Python, Scikit-learn, Data Analysis}}{June 2023 -- Aug 2023}
          \resumeItemListStart
            \resumeItem{Developed a predictive model for ADHD onset using smartwatch data, focusing on feature engineering and regression techniques.}
            \resumeItem{Visualized data insights using Matplotlib to support model findings and improve interpretability.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, C/C++, SQL, JavaScript, HTML/CSS} \\
     \textbf{Frameworks}{: Flutter, FastAPI, Scikit-learn} \\
     \textbf{Developer Tools}{: Git, Docker, Arduino, Vector Databases, FAISS} \\
     \textbf{Libraries}{: NumPy, Matplotlib, OpenAI GPT-4o-mini}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}